Analysis PPM-S

### 2020-04-22 production/prod_analysis-cfa.rmd

---
title: "Analysis PPM-S"
date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
css: "../input/bib/style.css"
output:
  html_document:
    number_sections: true
    toc: true
    toc_float:
        collapsed: false
    toc_depth: 2
    code_folding: "hide"
editor_options:
  chunk_output_type: console
---

@@

```{r eval=FALSE, include=FALSE}
rmarkdown::render(input = "production/prod_analysis-cfa.Rmd",output_format = "html_document"); browseURL(url = "production/prod_analysis-cfa.html")
```

@@

**Libraries**
```{r}
library(sjPlot)
library(dplyr)
library(lavaan)
library(semPlot)
library(stargazer)
library(corrplot)
library(psych)
library(knitr)
library(kableExtra)
```

@@

@@

@@

@@

@@

@@

## Correlations

@@

nodeNames <-c("Perception effort","Perception talent","Perception rich family","Perception networks",
              "Preference effort","Preference talent","Preference rich family","Preference networks",
              "Percepction meritocratic","Percepction non meritocratic","Preference meritocratic","Preference non meritocratic")

semPaths(plot01,
         style = "lisrel",
         fade=FALSE,
         edge.color = "black",
         nCharNodes = 0,
         curvePivot = FALSE,
         curve = 2,
         rotation = 4,
         layout = "tree3",
         cardinal = "lat cov",
         legend.cex = 0.6,
         label.cex =1,
         reorder = FALSE,
         nodeNames = nodeNames,
         nodeLabels = c("A","B","C","D","E","F","G","H","1","2","3","4"),
         label.font = 6,
         edge.label.font= 1,
         asize = 3, #arrow size
         edge.width =1,
         sizeMan=5,
         sizeLat = 10)
```

@@

# Save sumamry table wave 01------------------------------#
# as_image(sumtable01,file = "output/sumtablew01.png")
save_kable(sumtable01,file = "output/tables/sumtablew01.html",self_contained = FALSE)
```

@@

```{r}
model04 <- '
perc_merit =~ perc_effort+perc_talent
perc_nmerit=~perc_wpart +perc_netw
pref_merit =~ pref_effort+pref_talent
pref_nmerit=~pref_wpart +pref_netw'

fit4_c_mg <- cfa(model = model04,data = dat04,estimator="MLR",std.lv=FALSE,group = "grupo") # Continuous/ estimator ML Robust
fit4_o_mg <- cfa(model = model04,data = dat04,ordered = c("perc_effort","perc_talent",
                                                          "perc_wpart","perc_netw",
                                                          "pref_effort","pref_talent",
                                                          "pref_wpart","pref_netw"),std.lv=FALSE, group = "grupo")
#---------------------------------------------------#
kable(rbind(Continuous=fitmeasures(fit4_c_mg)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
            Ordinal=  fitmeasures(fit4_o_mg)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")]),
      format = "markdown",digits = 3,caption = "Fit indices")

cnames <- c("Grupo","Factor","Indicator","Loading (MLR)","Loading (DWLS)")
kable(left_join(x = standardizedsolution(fit4_c_mg) %>% filter(op=="=~") %>% select(group,lhs,rhs,est.std),
                y = standardizedsolution(fit4_o_mg) %>% filter(op=="=~") %>% select(group,lhs,rhs,est.std),
                c("group","lhs","rhs")),
      format = "markdown",digits = 2,col.names = cnames,caption = "Factor loadings by group")
```

@@

<!-- > **NOTE:** Cargas factoriales de segundo orden son bajas. El ajuste del modelo no es bueno. -->

@@

<!-- > **NOTE:** El modelo estimado con MLR con factores de segundo orden "meritocracia/ no meritocracia" no converge. EL modelo estimado a través de DWLS converge, posee cargas muy bajas y una muy alta (merit~pref_merit). Fit es malo (RMSEA >.10) -->

@@

# Wave 02 {.tabset .tabset-fade .tabset-pills}

Each sample correspond to one of the three conditions generated by the randomized assignment.

1. **Control group:** the group that has been assigned to the control group (placebo condition)

2. **Poverty condition sample** the group that has been assigned to the Poverty treatment condition.

3. **Inequality condition sample:** the group that has been assigned to the Inequality treatment condition.

4. **Complete sample:** Control, Poverty and Inequality treatment.

```{r}
data02 <- sjlabelled::read_spss(path = "input/data/original/Estudio_3_ola2.sav",verbose = FALSE)
load(file = "input/data/proc/datawide.RData")
dat01 <- data02 %>% select(starts_with("meritv03_p"))
```

**ATE on observed indicators**

```{r, out.width="75%",results='asis'}
m01<- lm(perc_effort_w2~treat,data = wide01)
m02<- lm(perc_talent_w2~treat,data = wide01)
m03<- lm(perc_wpart_w2~treat, data = wide01)
m04<- lm(perc_netw_w2~treat,  data = wide01)
#--------------------------------------------#
m05<- lm(pref_effort_w2~treat,data = wide01)
m06<- lm(pref_talent_w2~treat,data = wide01)
m07<- lm(pref_wpart_w2 ~treat, data = wide01)
m08<- lm(pref_netw_w2  ~treat,  data = wide01)
#--------------------------------------------#
stargazer::stargazer(m01,m02,m03,m04,type = "html")
stargazer::stargazer(m05,m06,m07,m08,type = "html")
```

<!-- > **NOTE**: Los tratamientos de información no se asocian de manera estadísticamente significativa con ninguno de los Indicatores de la escala de meritocracia.   -->

> **NOTE**: There are no statistically significant effects of the treatment conditions on the observed indicators of the meritocracy scale.

## Control group

```{r}
w02con <- data02 %>% filter(FL_6_DO_Control==1) %>% select(starts_with("meritv03_p"))
```

```{r results='asis'}
stargazer(w02con,type = "html",
          title = "Descriptive statistics",
          font.size = "small",
          median = TRUE,
          header=FALSE,
          digit.separator = "",
          digits = 2)
```

```{r}
corw02_1<-polychoric(w02con)
rownames(corw02_1$rho) <-c("1. pc_effort", "2. pc_talent","3. pc_wpart","4. pc_netw","5. pf_effort","6. pf_talent","7. pf_wpart", "8. pf_netw")
colnames(corw02_1$rho) <-c("(1)", "(2)","(3)","(4)","(5)","(6)","(7)", "(8)")
corrplot(corw02_1$rho,method = "color", type = "upper", tl.col = "black", addCoef.col = "black",diag = FALSE)
```

```{r,results='hold'}
model03 <- '
perc_merit=~meritv03_perc_effort+meritv03_perc_talent
perc_nmerit=~meritv03_perc_wpart+meritv03_perc_netw
pref_merit=~meritv03_pref_effort+meritv03_pref_talent
pref_nmerit=~meritv03_pref_wpart+meritv03_pref_netw'

fitw02a_c <- cfa(model = model03,data = w02con,estimator="MLR") # Continuous/ estimator ML Robust

fitw02a_o <- cfa(model = model03,data = w02con,ordered = c("meritv03_perc_effort","meritv03_perc_talent",
                                                           "meritv03_perc_wpart","meritv03_perc_netw",
                                                           "meritv03_pref_effort","meritv03_pref_talent",
                                                           "meritv03_pref_wpart","meritv03_pref_netw"))
#---------------------------------------------------#
kable(rbind(Continuous=fitmeasures(fitw02a_c)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
            Ordinal= fitmeasures(fitw02a_o)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")]),
      format = "markdown",digits = 3)

cnames <- c("Factor","Indicator","Loading (MLR)","Loading (DWLS)")
kable(left_join(x = standardizedsolution(fitw02a_c) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),
                y = standardizedsolution(fitw02a_o) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),
                c("lhs","rhs")),
      format = "markdown",digits = 2,col.names = cnames)
```

## Poverty condition

```{r}
w02pob <- data02 %>% filter(FL_6_DO_Tratamiento==1) %>% select(starts_with("meritv03_p"))
```

```{r results='asis'}
stargazer(w02pob,type = "html",
          title = "Descriptive statistics",
          font.size = "small",
          median = TRUE,
          header=FALSE,
          digit.separator = "",
          digits = 2)
```

```{r}
corw02_2<-polychoric(w02pob)
rownames(corw02_2$rho) <-c("1. pc_effort", "2. pc_talent","3. pc_wpart","4. pc_netw","5. pf_effort","6. pf_talent","7. pf_wpart", "8. pf_netw")
colnames(corw02_2$rho) <-c("(1)", "(2)","(3)","(4)","(5)","(6)","(7)", "(8)")
corrplot(corw02_2$rho,method = "color", type = "upper", tl.col = "black", addCoef.col = "black",diag = FALSE)
```

```{r,results='hold'}
model03 <- '
perc_merit=~meritv03_perc_effort+meritv03_perc_talent
perc_nmerit=~meritv03_perc_wpart+meritv03_perc_netw
pref_merit=~meritv03_pref_effort+meritv03_pref_talent
pref_nmerit=~meritv03_pref_wpart+meritv03_pref_netw'

fitw02b_c <- cfa(model = model03,data = w02pob,estimator="MLR") # Continuous/ estimator ML Robust

fitw02b_o <- cfa(model = model03,data = w02pob,ordered = c("meritv03_perc_effort","meritv03_perc_talent",
                                                           "meritv03_perc_wpart","meritv03_perc_netw",
                                                           "meritv03_pref_effort","meritv03_pref_talent",
                                                           "meritv03_pref_wpart","meritv03_pref_netw"))

#---------------------------------------------------#
kable(rbind(Continuous=fitmeasures(fitw02b_c)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
            Ordinal= fitmeasures(fitw02b_o)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")]),
      format = "markdown",digits = 3)

cnames <- c("Factor","Indicator","Loading (MLR)","Loading (DWLS)")
kable(left_join(x = standardizedsolution(fitw02b_c) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),
                y = standardizedsolution(fitw02b_o) %>% filter(op=="=~") %>% select(lhs,rhs,est.std),
                c("lhs","rhs")),
      format = "markdown",digits = 2,col.names = cnames)
```

## Inequality condition

```{r}
w02des <- data02 %>% filter(FL_6_DO_Tratamiento_desigualdad==1) %>% select(starts_with("meritv03_p"))
```

>>>>

---
title: "Analysis PPM-S"
date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
css: "../input/css/style.css"
output:
  html_document:
    number_sections: true
    toc: true
    toc_float:
        collapsed: false
    toc_depth: 2
    code_folding: "hide"
editor_options:
  chunk_output_type: console
---

@@

```{r eval=FALSE, include=FALSE}
rmarkdown::render(input = "production/prod_analysis-cfa.rmd",output_format = "html_document"); browseURL(url = "production/prod_analysis-cfa.html")
```

@@

**Libraries**
```{r}
library(sjPlot)
library(dplyr)
library(lavaan)
library(semPlot)
library(stargazer)
library(corrplot)
library(psych)
library(knitr)
library(kableExtra)
library(rvest)
source('production/prod_polychoric.R')
```

@@

```{r}
labs<- c("A. Who the more they try they manage to get bigger rewards that those who striveless.",
         "B. Who possess more talent they manage to obtain greater rewards than those who possess less talent.",
         "C. Who they have rich parents manage to get out ahead.",
         "D. Who they have good contacts they manage to get out ahead.",
         "E. Who the more they try they should get greater rewards than those who they try less." ,
         "F. Who possess more talent they should get greater rewards than those who possess less talent." ,
         "G. It's fine that those who have rich parents get ahead",
         "H. Is well that those who have good contacts get ahead." )
cnametab<- c("","(A)","(B)","(C)","(D)","(E)","(F)","(G)", "(H)","(1)","(2)","(3)","(4)","(1)","(2)","(3)","(4)")
```

```{r tabla01, eval=TRUE, include=TRUE}
polyw01<- poly(sjlabelled::remove_all_labels(dat01),
               digits = 2,
               triangle = "l",
               fade.ns = F,
               remove.spaces = T,
               string.diag = c("$-$","$-$","$-$","$-$","$-$","$-$","$-$","$-$"))
matpolyw01 <- as.data.frame(read_html(x = polyw01[["page.content"]]) %>% html_table(fill=FALSE)) 
matpolyw01 <- matpolyw01[-c(9),]
colnames(matpolyw01) <- c("vars","(A)","(B)","(C)","(D)","(E)","(F)","(G)","(H)")

load01<- data.frame(round(cbind(inspect(fit1_c,what="std")$lambda,inspect(fit1_o,what="std")$lambda),digits = 2))
load01[load01==c(0.00)] <- NA; names(load01) <- c(1:4,1:4)

table01<- bind_cols(x = matpolyw01,y = load01)
# %>% mutate(vars=labs)

kable(table01,escape = TRUE,align = "l",col.names = cnametab,format = "html") %>% 
  footnote(general = paste0(paste0("$N$= ",nobs(fit1_c)),"; p<0.05=$*$; p<0.01=$**$; p<0.001=$***$"),footnote_as_chunk = T) %>%
  add_header_above(c(" " = 1,"Polychoric correlations"=8, "MLR" = 4, "DWLS" = 4))%>%
  add_header_above(c(" " = 9,"Factor loadings"=8)) %>%
  column_spec(column = c(1),width ="7in",include_thead = T) %>%
  column_spec(column = c(2:17),width ="0.5in",include_thead = T) %>% 
  kable_styling(full_width = FALSE)
```

@@

```{r tabla02, echo=FALSE, include=TRUE}
polyw02<- poly(sjlabelled::remove_all_labels(dat02),
               digits = 2,
               triangle = "l",
               fade.ns = F,
               remove.spaces = T,
               string.diag = c("$-$","$-$","$-$","$-$","$-$","$-$","$-$","$-$"))
matpolyw02 <- as.data.frame(read_html(x = polyw02[["page.content"]]) %>% html_table(fill=FALSE)) 
matpolyw02 <- matpolyw02[-c(9),] 
colnames(matpolyw02) <- c("vars","(A)","(B)","(C)","(D)","(E)","(F)","(G)", "(H)")

load02<- data.frame(round(cbind(inspect(fit2_c,what="std")$lambda,inspect(fit2_o,what="std")$lambda),digits = 2))
load02[load02==c(0.00)] <- NA; names(load02) <- c(1:4,1:4)

table02<- bind_cols(x = matpolyw02,y = load02)
# %>% mutate(vars=labs)

kable(table02,escape = FALSE,align = "l",col.names = cnametab)  %>% 
  footnote(general = paste0(paste0("$N$= ",nobs(fit2_c)),"; p<0.05=$*$; p<0.01=$**$; p<0.001=$***$"),footnote_as_chunk = T) %>%
  add_header_above(c(" " = 1,"Polychoric correlations"=8, "MLR" = 4, "DWLS" = 4))%>% 
  add_header_above(c(" " = 9,"Factor loadings"=8)) %>% 
  column_spec(column = c(1),width ="7in",include_thead = T) %>%
  column_spec(column = c(2:17),width ="0.5in",include_thead = T) %>% 
  kable_styling(full_width = FALSE) %>% 
  kable_styling(full_width = F)
```

@@

```{r}
polyw03<- poly(sjlabelled::remove_all_labels(dat03),
               digits = 2,
               triangle = "l",
               fade.ns = F,
               remove.spaces = T,
               string.diag = c("$-$","$-$","$-$","$-$","$-$","$-$","$-$","$-$"))
matpolyw03 <- as.data.frame(read_html(x = polyw03[["page.content"]]) %>% html_table(fill=FALSE)) 
matpolyw03 <- matpolyw03[-c(9),]

colnames(matpolyw03) <- c("vars","(A)","(B)","(C)","(D)","(E)","(F)","(G)", "(H)")

load03<- data.frame(round(cbind(inspect(fit3_c,what="std")$lambda,inspect(fit3_o,what="std")$lambda),digits = 2))
load03[load03==c(0.00)] <- NA; names(load03) <- c(1:4,1:4)

table03<- bind_cols(x = matpolyw03,y = load03)
# %>% mutate(vars=labs)

kable(table03,escape = FALSE,align = "l",col.names = cnametab) %>% 
  footnote(general = paste0(paste0("$N$= ",nobs(fit3_c)),"; p<0.05=$*$; p<0.01=$**$; p<0.001=$***$"),footnote_as_chunk = T) %>%
  add_header_above(c(" " = 1,"Polychoric correlations"=8, "MLR" = 4, "DWLS" = 4))%>% 
  add_header_above(c(" " = 9,"Factor loadings"=8)) %>% 
  column_spec(column = c(1),width ="7in",include_thead = T) %>%
  column_spec(column = c(2:17),width ="0.5in",include_thead = T) %>% 
  kable_styling(full_width = F)
```

@@

```{r tabla03, include=FALSE}
polyw03tau<- poly(sjlabelled::remove_all_labels(dat03),
               digits = 2,
               triangle = "l",
               fade.ns = F,
               remove.spaces = T,
               string.diag = c("$-$","$-$","$-$","$-$","$-$","$-$","$-$","$-$"))
matpolyw03tau <- as.data.frame(read_html(x = polyw03tau[["page.content"]]) %>% html_table(fill=FALSE)) 
matpolyw03tau <- matpolyw03tau[-c(9),]

colnames(matpolyw03tau) <- c("vars","(A)","(B)","(C)","(D)","(E)","(F)","(G)", "(H)") 
load03tau<- data.frame(round(cbind(inspect(fit3_c.tau,what="std")$lambda,inspect(fit3_o.tau,what="std")$lambda),digits = 2))
load03tau[load03tau==c(0.00)] <- NA; names(load03tau) <- c(1:4,1:4)

table03tau<- bind_cols(x = matpolyw03tau,y = load03tau) 
# %>% mutate(vars=labs)

kable(table03tau,escape = FALSE,align = "l",col.names = cnametab) %>% 
  footnote(general = paste0(paste0("$N$= ",nobs(fit3_c.tau)),"; p<0.05=$*$; p<0.01=$**$; p<0.001=$***$"),footnote_as_chunk = T) %>%
  add_header_above(c(" " = 1,"Polychoric correlations"=8, "MLR" = 4, "DWLS" = 4))%>% 
  add_header_above(c(" " = 9,"Factor loadings"=8)) %>% 
  column_spec(column = c(1),width ="7in",include_thead = T) %>%
  column_spec(column = c(2:17),width ="0.5in",include_thead = T) %>% 
  kable_styling(full_width = F)
```

@@

```{r tabla04, include=FALSE}
polyw04<- poly(sjlabelled::remove_all_labels(dat04[,-c(1)]),
               digits = 2,
               triangle = "l",
               fade.ns = F,
               remove.spaces = T,
               string.diag = c("$-$","$-$","$-$","$-$","$-$","$-$","$-$","$-$"))
matpolyw04 <- as.data.frame(read_html(x = polyw04[["page.content"]]) %>% html_table(fill=FALSE)) 
matpolyw04 <- matpolyw04[-c(9),]

colnames(matpolyw04) <- c("vars","(A)","(B)","(C)","(D)","(E)","(F)","(G)", "(H)") 
load04<- data.frame(round(cbind(inspect(fit4_c,what="std")$lambda,inspect(fit4_o,what="std")$lambda),digits = 2))
load04[load04==c(0.00)] <- NA; names(load04) <- c(1:4,1:4)

table04<- bind_cols(x = matpolyw04,y = load04) 
# %>% mutate(vars=labs)

kable(table04,escape = FALSE,align = "l",col.names = cnametab) %>% 
  footnote(general = paste0(paste0("$N$= ",nobs(fit4_c)),"; p<0.05=$*$; p<0.01=$**$; p<0.001=$***$"),footnote_as_chunk = T) %>%
  add_header_above(c(" " = 1,"Polychoric correlations"=8, "MLR" = 4, "DWLS" = 4))%>% 
  add_header_above(c(" " = 9,"Factor loadings"=8)) %>% 
  column_spec(column = c(1),width ="7in",include_thead = T) %>%
  column_spec(column = c(2:17),width ="0.5in",include_thead = T) %>% 
  kable_styling(full_width = F)
```

# Tables

```{r tb_desc-corr}
load04<- data.frame(round(inspect(fit4_o,what="std")$lambda,digits = 2))
load04[load04==c(0.00)] <- NA; names(load04) <- c(1:4)

colnames(matpolyw04) <- c("Variable","A","B","C","D","E","F","G", "H")

sum04b  <- psych::describe(dat04[,-c(1)], fast = T) %>% select(mean,sd,min,max) %>% data.frame() %>% round(digits = 2)
table04b<- bind_cols(x = sum04b,y = matpolyw04) %>% select(Variable, everything()) %>% mutate(Variable=labs) %>% rename("Mean"=mean, "SD"=sd, "Min"=min,"Max"=max)

cap01 <- "Descriptive statistic"
sumdat04<- kable(table04b, escape = FALSE,align = "l",linesep = "", caption = cap01) %>% 
           column_spec(column = 1,width = "10cm",width_min = "12cm",include_thead = TRUE) %>% 
           footnote(general = paste0(paste0("$N$= ","2141"),"; p<0.05=$*$; p<0.01=$**$; p<0.001=$***$"),footnote_as_chunk = T) %>% 
           add_header_above(header = c(" "=5,"Polychoric correlations"= 8)) %>% 
           kable_styling(full_width = TRUE,font_size = 8,position = "center");sumdat04
save(sumdat04,file = "output/tables/sumdat04.RData")
```

```{r tb_loads-fitm}
tb.load<- data.frame(round(cbind(inspect(fit1_o,what="std")$lambda,
                                 inspect(fit2_o,what="std")$lambda,
                                 inspect(fit3_o,what="std")$lambda),
                           digits = 2))
tb.load[tb.load==c(0.00)] <- NA; names(tb.load) <- c(paste0("M1.",1:4),paste0("M2.",1:4),paste0("M3.",1:4))

for (i in names(tb.load)) {
  # tb.load[,i] <- sjlabelled::as_character(tb.load[,i])
  tb.load[,i] <- sprintf(tb.load[,i], fmt = '%#.2f')
}
tb.load[tb.load=="NA"] <- ""

#-------#
fm01<- data.frame(t(data.frame(fitmeasures(fit1_o, output ="matrix")[c("chisq.scaled","df","cfi.scaled","rmsea.scaled"),]))); row.names(fm01) ="M1.1"
fm02<- data.frame(t(data.frame(fitmeasures(fit2_o, output ="matrix")[c("chisq.scaled","df","cfi.scaled","rmsea.scaled"),]))); row.names(fm02) ="M2.1"
fm03<- data.frame(t(data.frame(fitmeasures(fit3_o, output ="matrix")[c("chisq.scaled","df","cfi.scaled","rmsea.scaled"),]))); row.names(fm03) ="M3.1"

#------chi2, df------#
fm04<- round(rbind(fm01,fm02,fm03),3)
fm04.1 <- fm04 %>% select(chisq.scaled,df) 
fm04.1$chisq.scaled <- round(x = fm04.1$chisq.scaled,digits = 2)
fm04.1$df <- round(x = fm04.1$df,digits = 0)
fm04.1$chi2df <- paste0(fm04.1$chisq.scaled,"(",fm04.1$df,")")
fm04.1 <- select(fm04.1,"chi2df")
for (i in names(fm04.1)) {
  fm04.1[,i] <- as.character(fm04.1[,i])
}

#------CFI, RMSEA------#
fm04.2 <- fm04 %>% select(cfi.scaled,rmsea.scaled) 
for (i in names(fm04.2)) {
  fm04.2[,i] <- sprintf(fm04.2[,i], fmt = '%#.3f')
}

fm.df      <- bind_cols(fm04.1,fm04.2)
fm.df$nobs <- c(nobs(fit1_o),nobs(fit2_o),nobs(fit3_o)) 
fm.df <- data.frame(t(fm.df)); colnames(fm.df) <- c("M1.1","M2.1","M3.1")
#------ merge ------#
tb.fm<- bind_rows(tb.load,fm.df)
tb.fm<- tb.fm %>% mutate(vars=c(labs,"$\\chi^2\\text{(df)}$","$\\text{CFI}$","$\\text{RMSEA}$","$N$")) %>% select(vars,everything())
#--table---#
tb.col  <- c("Variables",1:4,1:4,1:4)
tb.foot <- paste0("; p<0.05=$*$; p<0.01=$**$; p<0.001=$***$. Standardised factor loadings using DWLS estimator. CFI = Comparative fit index (scaled), RMSEA = Root mean square error of approximation (scaled)")
tb.caption <- "Factor loadings and fit measures"

tb.fm01<- kable(tb.fm,escape = FALSE,align = "lcccccccccccc",col.names = tb.col, caption = tb.caption) %>% 
          kable_styling(full_width = F,font_size = 9) %>% 
          column_spec(column = 1,width = "10cm",width_min = "12cm",include_thead = TRUE) %>% 
          column_spec(column = 2:13,width = "1cm",width_min = "1.3cm",include_thead = TRUE) %>% 
          add_header_above(header = c(" "=1,"Version 1"= 4,"Version 2"= 4,"Version 3"= 4)) %>% 
          add_header_above(header = c(" "=1,"Factor loadings"= 12)) %>% 
          row_spec(row = 8,hline_after = TRUE) %>%
          add_indent(c(9:12)) %>% 
          footnote(general =tb.foot ,footnote_as_chunk = T);tb.fm01
save(tb.fm01,file = "output/tables/tb.fm01.RData")
```

@@

## Correlations plots

@@

nodeNames <-c("Perception effort","Perception talent","Perception rich family","Perception networks",
              "Preference effort","Preference talent","Preference rich family","Preference networks",
              "Perception meritocratic","Perception non meritocratic","Preference meritocratic","Preference non meritocratic")

semPaths(plot01,
         style = "lisrel",
         fade=FALSE,
         edge.color = "black",
         nCharNodes = 0,
         curvePivot = FALSE,
         curve = 2,
         rotation = 4,
         layout = "tree3",
         cardinal = "lat cov",
         legend.cex = 0.6,
         label.cex =1,
         reorder = FALSE,
         nodeNames = nodeNames,
         nodeLabels = c("A","B","C","D","E","F","G","H","1","2","3","4"),
         label.font = 6,
         edge.label.font= 1,
         asize = 3, #arrow size
         edge.width =1,
         sizeMan=5,
         sizeLat = 10,
         filetype ="png",
         width = 12,
         height= 10,
         filename = "output/images/meas01")
```

![](../output/images/meas01.png)

@@

# Save sumamry table wave 01------------------------------#
# as_image(sumtable01,file = "output/sumtablew01.png")
# save_kable(sumtable01,file = "output/tables/sumtablew01.html",self_contained = FALSE)
```

@@

```{r}
model04 <- '
perc_merit =~ perc_effort + perc_talent
perc_nmerit=~ perc_wpart  + perc_netw
pref_merit =~ pref_effort + pref_talent
pref_nmerit=~ pref_wpart  + pref_netw'

fit4_c_mg <- cfa(model = model04,data = dat04,estimator="MLR",std.lv=FALSE,group = "grupo") # Continuous/ estimator ML Robust
fit4_o_mg <- cfa(model = model04,data = dat04,ordered = c("perc_effort","perc_talent",
                                                          "perc_wpart","perc_netw",
                                                          "pref_effort","pref_talent",
                                                          "pref_wpart","pref_netw"),std.lv=FALSE, group = "grupo")
#---------------------------------------------------#
kable(rbind(Continuous=fitmeasures(fit4_c_mg)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")],
            Ordinal=  fitmeasures(fit4_o_mg)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")]),
      format = "markdown",digits = 3,caption = "Fit indices")
gr01=standardizedsolution(fit4_c_mg) %>% filter(op=="=~") %>% select(group,lhs,rhs,est.std)
gr02=standardizedsolution(fit4_o_mg) %>% filter(op=="=~") %>% select(group,lhs,rhs,est.std)
gr01$group=dplyr::recode(gr01$group, `1` = "mod03", `2` = "mod02", `3` = "mod01")
gr02$group=dplyr::recode(gr02$group, `1` = "mod03", `2` = "mod02", `3` = "mod01")

cnames <- c("Grupo","Factor","Indicator","Loading (MLR)","Loading (DWLS)")
kable(left_join(x =gr01 ,
                y =gr02 ,
                c("group","lhs","rhs")),
      format = "markdown",digits = 2,col.names = cnames,caption = "Factor loadings by group")
```

@@

@@

@@

<!-- # Wave 02 {.tabset .tabset-fade .tabset-pills} -->

<!-- Each sample correspond to one of the three conditions generated by the randomized assignment. -->

<!-- 1. **Control group:** the group that has been assigned to the control group (placebo condition) -->

<!-- 2. **Poverty condition sample** the group that has been assigned to the Poverty treatment condition. -->

<!-- 3. **Inequality condition sample:** the group that has been assigned to the Inequality treatment condition. -->

<!-- 4. **Complete sample:** Control, Poverty and Inequality treatment. -->

<!-- ```{r} -->
<!-- data02 <- sjlabelled::read_spss(path = "input/data/original/Estudio_3_ola2.sav",verbose = FALSE) -->
<!-- load(file = "input/data/proc/datawide.RData") -->
<!-- dat01 <- data02 %>% select(starts_with("meritv03_p")) -->
<!-- ``` -->

<!-- **ATE on observed indicators** -->

<!-- ```{r, out.width="75%",results='asis'} -->
<!-- m01<- lm(perc_effort_w2~treat,data = wide01) -->
<!-- m02<- lm(perc_talent_w2~treat,data = wide01) -->
<!-- m03<- lm(perc_wpart_w2~treat, data = wide01) -->
<!-- m04<- lm(perc_netw_w2~treat,  data = wide01) -->
<!-- #--------------------------------------------# -->
<!-- m05<- lm(pref_effort_w2~treat,data = wide01) -->
<!-- m06<- lm(pref_talent_w2~treat,data = wide01) -->
<!-- m07<- lm(pref_wpart_w2 ~treat, data = wide01) -->
<!-- m08<- lm(pref_netw_w2  ~treat,  data = wide01) -->
<!-- #--------------------------------------------# -->
<!-- stargazer::stargazer(m01,m02,m03,m04,type = "html") -->
<!-- stargazer::stargazer(m05,m06,m07,m08,type = "html") -->
<!-- ``` -->

<!-- > **NOTE**: There are no statistically significant effects of the treatment conditions on the observed indicators of the meritocracy scale. -->

<!-- ## Control group -->

<!-- ```{r} -->
<!-- w02con <- data02 %>% filter(FL_6_DO_Control==1) %>% select(starts_with("meritv03_p")) -->
<!-- ``` -->

<!-- ```{r results='asis'} -->
<!-- stargazer(w02con,type = "html", -->
<!--           title = "Descriptive statistics", -->
<!--           font.size = "small", -->
<!--           median = TRUE, -->
<!--           header=FALSE, -->
<!--           digit.separator = "", -->
<!--           digits = 2) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- corw02_1<-polychoric(w02con) -->
<!-- rownames(corw02_1$rho) <-c("1. pc_effort", "2. pc_talent","3. pc_wpart","4. pc_netw","5. pf_effort","6. pf_talent","7. pf_wpart", "8. pf_netw") -->
<!-- colnames(corw02_1$rho) <-c("(1)", "(2)","(3)","(4)","(5)","(6)","(7)", "(8)") -->
<!-- corrplot(corw02_1$rho,method = "color", type = "upper", tl.col = "black", addCoef.col = "black",diag = FALSE) -->
<!-- ``` -->

<!-- ```{r,results='hold'} -->
<!-- model03 <- ' -->
<!-- perc_merit=~meritv03_perc_effort+meritv03_perc_talent -->
<!-- perc_nmerit=~meritv03_perc_wpart+meritv03_perc_netw -->
<!-- pref_merit=~meritv03_pref_effort+meritv03_pref_talent -->
<!-- pref_nmerit=~meritv03_pref_wpart+meritv03_pref_netw' -->

<!-- fitw02a_c <- cfa(model = model03,data = w02con,estimator="MLR") # Continuous/ estimator ML Robust -->

<!-- fitw02a_o <- cfa(model = model03,data = w02con,ordered = c("meritv03_perc_effort","meritv03_perc_talent", -->
<!--                                                            "meritv03_perc_wpart","meritv03_perc_netw", -->
<!--                                                            "meritv03_pref_effort","meritv03_pref_talent", -->
<!--                                                            "meritv03_pref_wpart","meritv03_pref_netw")) -->
<!-- #---------------------------------------------------# -->
<!-- kable(rbind(Continuous=fitmeasures(fitw02a_c)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")], -->
<!--             Ordinal= fitmeasures(fitw02a_o)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")]), -->
<!--       format = "markdown",digits = 3) -->

<!-- cnames <- c("Factor","Indicator","Loading (MLR)","Loading (DWLS)") -->
<!-- kable(left_join(x = standardizedsolution(fitw02a_c) %>% filter(op=="=~") %>% select(lhs,rhs,est.std), -->
<!--                 y = standardizedsolution(fitw02a_o) %>% filter(op=="=~") %>% select(lhs,rhs,est.std), -->
<!--                 c("lhs","rhs")), -->
<!--       format = "markdown",digits = 2,col.names = cnames) -->
<!-- ``` -->

<!-- ## Poverty condition -->

<!-- ```{r} -->
<!-- w02pob <- data02 %>% filter(FL_6_DO_Tratamiento==1) %>% select(starts_with("meritv03_p")) -->
<!-- ``` -->

<!-- ```{r results='asis'} -->
<!-- stargazer(w02pob,type = "html", -->
<!--           title = "Descriptive statistics", -->
<!--           font.size = "small", -->
<!--           median = TRUE, -->
<!--           header=FALSE, -->
<!--           digit.separator = "", -->
<!--           digits = 2) -->
<!-- ``` -->

<!-- ```{r} -->
<!-- corw02_2<-polychoric(w02pob) -->
<!-- rownames(corw02_2$rho) <-c("1. pc_effort", "2. pc_talent","3. pc_wpart","4. pc_netw","5. pf_effort","6. pf_talent","7. pf_wpart", "8. pf_netw") -->
<!-- colnames(corw02_2$rho) <-c("(1)", "(2)","(3)","(4)","(5)","(6)","(7)", "(8)") -->
<!-- corrplot(corw02_2$rho,method = "color", type = "upper", tl.col = "black", addCoef.col = "black",diag = FALSE) -->
<!-- ``` -->

<!-- ```{r,results='hold'} -->
<!-- model03 <- ' -->
<!-- perc_merit=~meritv03_perc_effort+meritv03_perc_talent -->
<!-- perc_nmerit=~meritv03_perc_wpart+meritv03_perc_netw -->
<!-- pref_merit=~meritv03_pref_effort+meritv03_pref_talent -->
<!-- pref_nmerit=~meritv03_pref_wpart+meritv03_pref_netw' -->

<!-- fitw02b_c <- cfa(model = model03,data = w02pob,estimator="MLR") # Continuous/ estimator ML Robust -->
